
-------------------------------------------
1.	Perform Summary Analysis describing the number of 
    a.	Columns
    b.	rows 
    c.	names of different columns
    d.	The class types of the columns
    
```{r}

#Super_Store <- read.csv("EDA/Hackathon/Data 2.csv",header = TRUE)
Super_Store <- read.csv(file.choose(),header = TRUE)
Store_Data <- Super_Store

dim(Store_Data)
names(Store_Data)
str(Store_Data)

head(Store_Data,3)
summary(Store_Data)
class(Store_Data)

```

2.	Check the Data Quality of the data. If you realize there are null values in it, use Data Imputation for filling the data. Justify the methodology you follow for Data Imputaion. 

```{r}

Store_Data <- subset(Store_Data,Store_Data$Sales != "")
dim(Store_Data)

sum(is.na(Store_Data))
colSums(is.na(Store_Data))

```

3.	Do Univariate Analysis of all the variables present.

```{r}

library(ggplot2)
library(reshape2)

#=============================================================
# Ship Mode Column Univariate Analysis

tab = table(Store_Data$Ship.Mode)
vec1 <- tab[names(tab)]
vec1 <- as.vector(vec1)

bar = barplot(tab,col=rainbow(length(vec1)),ylim = c(0,max(vec1)+5000),main = "Shipping Mode Distribution",xlab = "Shipping Mode",ylab = "Order Frequency")
text(x = bar, y = vec1, label = vec1, pos = 3, cex = 1, col = rainbow(length(vec1)))

x <- vec1
labels <-  names(tab)
piepercent<- round(100*x/sum(x), 1)

pie(x, labels = piepercent, main = "Shipping Mode Distribution",col = rainbow(length(x)))
legend("topleft", labels, cex = 0.8,fill = rainbow(length(x)))

#=============================================================
# Segment Column Univariate Analysis

tab = table(Store_Data$Segment)
vec1 <- tab[names(tab)]
vec1 <- as.vector(vec1)

bar = barplot(tab,col=rainbow(length(vec1)),ylim = c(0,max(vec1)+5000),main = "Segment Distribution",xlab = "Segment",ylab = "Order Frequency")
text(x = bar, y = vec1, label = vec1, pos = 3, cex = 1, col = rainbow(length(vec1)))

x <- vec1
labels <-  names(tab)

piepercent<- round(100*x/sum(x), 1)
pie1 <- pie(x, labels = piepercent, main = "Segment Distribution",col = rainbow(length(x)))
legend("topleft", labels, cex = 0.8,fill = rainbow(length(x)))

#=============================================================
#Univariate Analysis for Order Date

data_Date <- Store_Data[,c('Order.ID','Order.Date')]

data_Date = data_Date[!duplicated(data_Date$Order.ID),]
dt <- as.Date(data_Date$Order.Date, format = "%d-%m-%y")

FuncQuarter <- function(a) ceiling(as.integer(format(as.Date(a), "%m"))/3)
quar <- lapply(dt, function(y) FuncQuarter(y) )
quar <- as.vector(unlist(quar))
data_Date$Quarter <- quar

FuncYear <- function(a) as.integer(format(as.Date(a), "%Y"))
Y1 <- lapply(dt, function(y) FuncYear(y) )
Y1 <- as.vector(unlist(Y1))
data_Date$Year <- Y1

tab = table(data_Date$Quarter)
vec1 <- tab[names(tab)]
vec1 <- as.vector(vec1)

bar = barplot(tab,col=rainbow(length(vec1)),ylim = c(0,max(vec1)+2000),main = "Quarter wise Order", xlab = "Quarter",ylab = "Order Frequency")
text(x = bar, y = vec1, label = vec1, pos = 3, cex = 1, col = rainbow(length(vec1)))

x <- vec1
labels <-names(tab)

piepercent<- round(100*x/sum(x), 1)
pie(x, labels = piepercent, main = "Quarter wise Order",col = rainbow(length(x)))
legend("topleft", labels, cex = 0.6,fill = rainbow(length(x)))

tab = table(data_Date$Year)
vec1 <- tab[names(tab)]
vec1 <- as.vector(vec1)

bar = barplot(tab,col=rainbow(length(vec1)),ylim = c(0,max(vec1)+2000),main = "Year wise Order", xlab = "Year",ylab = "Order Frequency")
text(x = bar, y = vec1, label = vec1, pos = 3, cex = 1, col = rainbow(length(vec1)))

x <- vec1
labels <-names(tab)

piepercent<- round(100*x/sum(x), 1)
pie(x, labels = piepercent, main = "Year wise Order",col = rainbow(length(x)))
legend("topleft", labels, cex = 0.6,fill = rainbow(length(x)))

#=============================================================
#Univariant Analysis Category

Category <- table(Store_Data$Category)
a <-prop.table(Category)
b <-levels(Store_Data$Category)
lable_cat <- round(c(a*100),2)

pie(a,labels = lable_cat, col = rainbow(length(a)),radius = 1)
legend("topleft",b,cex = 0.8,fill = rainbow(length(a)))

#=============================================================
#Univariant Analysis Sub-Category

Sub.Category <- table(Store_Data$Sub.Category)
c <- prop.table(Sub.Category)
d <- levels(Store_Data$Sub.Category)
lable_sub.cat <- round(c(c*100),2)

pie(c, labels = lable_sub.cat,col = c(5:30,2),radius = 1)
legend("topleft",d,cex = 0.7,fill = c(5:30,2))
 
#=============================================================
#Univatiant Analysis Order Priority

order_priority <- table(Store_Data$Order.Priority)
e <- prop.table(order_priority)
f <- levels(Store_Data$Order.Priority)
lable_order <- round(c(e*100),2)

pie(e,labels = lable_order, col = rainbow(length(e)),radius = 1)
legend("topleft",f,cex = 0.8,fill = rainbow(length(e)))

#=============================================================
# Univatiant Analysis Market

market <- table(Store_Data$Market)
g <- prop.table(market)
h <- levels(Store_Data$Market)
lable_market <- round(c(g*100),2)

pie(g,labels = lable_market, col = rainbow(length(g)),radius = 1)
legend("topleft",h,cex = 0.8,fill = rainbow(length(g)))

#=============================================================
# Pie chart for region

#regionTab<-table(Store_Data$Region)
#a <-prop.table(x)
#b<-levels(Store_Data$Region)
#label_region <- round(c(a*100),2)

#pie(a, labels = label_region, col= rainbow(length(a)),radius=1)
#legend("topleft", b, cex=0.7, fill = rainbow(length(a)))

#=============================================================
# Pie chart for country

#CountryTab<-table(Store_Data$Country)
#c <-prop.table(x)
#d<-levels(Store_Data$Country)
#label_country <- round(c(a*100),2)

#pie(c, labels = label_country, col= rainbow(length(c)),radius=1)
#legend("topleft", d, cex=0.7, fill = rainbow(length(c)))

```

4.	The target variables in this dataset is the attribute "Sales" Do a bivariate analysis of this variable with all the other attributes. Also give your inferences from the graph generated.

```{r}

#=============================================================
# Bivarite analysis for Categoty and Sale

cat_sal <- Store_Data[,c('Category','Sales')]

sale <- as.character(cat_sal$Sales)
#sale <- substr(sale, 2, nchar(sale))
sale <- gsub("\\$", "", sale)
sale <- gsub(",","",sale)
sale <- as.numeric(sale)

cat_sal$NewSale <- sale
cat_sal$Sales <- NULL

d1 <- aggregate(NewSale~Category, data=cat_sal, FUN=sum) 

tab = table(data_Date$Year)
vec1 <- d1$NewSale
vec1 <- as.vector(vec1)

x <- vec1
labels <- as.vector(d1$Category)

piepercent<- round(100*x/sum(x), 1)
pie(x, labels = piepercent, main = "Sales by Category",col = rainbow(length(x)))
legend("topleft", labels, cex = 0.8,fill = rainbow(length(x)))

#=============================================================
#Bivariate analysis for Order date and Sale

date_sale <- Store_Data[,c('Order.Date','Sales')]
date_sale$NewSale <- sale
date_sale$Sales <- NULL

dt <- as.Date(date_sale$Order.Date, format = "%d-%m-%y")

FuncQuarter <- function(a) ceiling(as.integer(format(as.Date(a), "%m"))/3)
quar <- lapply(dt, function(y) FuncQuarter(y) )
quar <- as.vector(unlist(quar))
date_sale$Quarter <- quar

FuncYear <- function(a) as.integer(format(as.Date(a), "%Y"))
Y1 <- lapply(dt, function(y) FuncYear(y) )
Y1 <- as.vector(unlist(Y1))
date_sale$Year <- Y1

d1 <- aggregate(NewSale~Year+Quarter, data=date_sale, FUN=sum) 
QT <- paste0("Q",d1$Quarter)
d1$NewQu <- QT

names(d1)[names(d1) == 'NewSale'] <- 'Sale'
names(d1)[names(d1) == 'NewQu'] <- 'Quarters'

ggplot(data = d1, aes(x=Year, y=Sale)) + geom_line(aes(colour=Quarters)) + geom_point(aes(colour=Quarters))

#ggplot(data = d1, aes(x=Year, y=NewSale)) + geom_line(aes(colour=NewQu)) + geom_point(aes(colour=NewQu))

#=============================================================
# Bivariate analysis for Product and Sale

sale_pro <- Store_Data[,c('Product.ID','Sales')]
sale_pro$NewSale <- sale
sale_pro$Sales <- NULL

d1 <- aggregate(NewSale~Product.ID, data=sale_pro, FUN=sum) 

d2 <- d1[with(d1, order(-NewSale)), ]
Top10Product <- head(d2,10)
Bottom10Product <- tail(d2,10)

Top10Product
Bottom10Product

#=============================================================
# BiVariant Analysis Sales Vs Sub_Categories

sales <- gsub(",", "", Store_Data$Sales)
sales <- as.numeric(gsub("\\$", "", sales)) 
Store_Data$new_sales <- sales

ggplot(Store_Data, aes(Sub.Category , new_sales))+
  ylab("Sales in Dollars($)")+
  xlab("Product Sub_Categories")+
  ggtitle("Sales from different Sub_Categories")+
  theme(plot.title = element_text(hjust = 0.5,size = 18,face = "bold"))+
  geom_bar(stat = "identity",fill = "#6666FF")+ 
  coord_flip()

#=============================================================
# BiVariant Analysis Sales Vs Region

ggplot(Store_Data, aes(Region, new_sales))+
  ylab("Sales in Dollars($)")+
  xlab("Business Regions")+
  ggtitle("Sales from different Business Regions")+
  theme(plot.title = element_text(hjust = 0.5,size = 18,face = "bold"))+
  geom_bar(stat = "identity",fill = "#6666FF")+ 
  coord_flip()

#=============================================================
# BiVariant Analysis Sales Vs Countries

#ggplot(Store_Data, aes(Country, new_sales))+
#  ylab("Sales in Dollars($)")+
#  xlab("Business Countries")+
#  ggtitle("Sales from different Business Countries")+
#  theme(plot.title = element_text(hjust = 0.5,size = 18,face = "bold"))+
#  geom_bar(stat = "identity",fill = "#6666FF")+ 
#  coord_flip() #Output not clear

#Going for top 10 countries

aggr_country <-aggregate(Store_Data$new_sales, by=list(Category=Store_Data$Country), FUN=sum)
sorted_aggr <-aggr_country[order(-aggr_country$x),c(1,2)]

top <- head(sorted_aggr,10)
ggplot(data = top, aes(x = Category, x))+
  geom_bar(stat = "identity",fill = "#6666FF")+
  coord_flip()+
  ylab("Sales in Dollars($)")+
  xlab("Business Countries")+
  ggtitle("Top 10 Countries(Sales)")+
  theme(plot.title = element_text(hjust = 0.5,size = 18,face = "bold"))

# Going for bottom 10 countries

bottom <- tail(sorted_aggr,10)
ggplot(data = bottom, aes(x = Category, x))+
  geom_bar(stat = "identity",fill = "#6666FF")+
  coord_flip()+
  ylab("Sales in Dollars($)")+
  xlab("Business Countries")+
  ggtitle("Bottom 10 Countries(Sales)")+
  theme(plot.title = element_text(hjust = 0.5,size = 18,face = "bold"))

#=============================================================
# Bar plot for region vs Count of purchased products

Store_Data$Region = as.factor(Store_Data$Region)
Store_Data$Country = as.factor(Store_Data$Country)
Store_Data$Ship.Mode = as.factor(Store_Data$Ship.Mode)

p <- ggplot(Store_Data, aes(x=Region))+geom_bar(fill= "red")+ theme_bw() +labs(y="no. of products", title = "Region most products purchased")
p+theme(axis.text.x =element_text(angle=90, hjust=1) )

#=============================================================
# Plot for Ship Mode vs Sales

sales <- gsub(",", "", Store_Data$Sales)
sales <- as.numeric(gsub("\\$", "", sales)) 
Store_Data$new_sales <- sales

ggplot(Store_Data, aes(Ship.Mode , new_sales))+
  ylab("Sales in Dollars($)")+
  xlab("Ship Mode")+
  ggtitle("Sales vs Ship Mode")+
  theme(plot.title = element_text(hjust = 0.5,size = 18,face = "bold"))+
  geom_bar(stat = "identity",fill = "#6666FF")+ 
  coord_flip()

#=============================================================
# Plot for Segment vs Sales

ggplot(Store_Data, aes(Segment , new_sales))+
  ylab("Sales in Dollars($)")+
  xlab("Segment")+
  ggtitle("Sales vs Segment")+
  theme(plot.title = element_text(hjust = 0.5,size = 18,face = "bold"))+
  geom_bar(stat = "identity",fill = "#6666FF")+ 
  coord_flip()

#=============================================================
#Aggregation Profit vs Product

profit <-  gsub("-.*", "", Store_Data$Profit)
profit <- gsub(",", "", Store_Data$Profit)
profit <- as.numeric(gsub("\\$", "", profit))

sales <- gsub(",", "", Store_Data$Sales)
sales <- as.numeric(gsub("\\$", "", sales))

Store_Data$new_sales <- sales
Store_Data$new_profit <- profit

aggr_prodName <-aggregate(Store_Data$new_profit,  by=list(Product=Store_Data$Product.Name), FUN=sum)
sorted_prodName <-aggr_prodName[order(-aggr_prodName$x),c(1,2)]
top_prodName <- head(sorted_prodName,10)

x <-ggplot(data = top_prodName, aes(x = Product, x))+
  geom_point(stat = "identity")+
  ylab("Profit in Dollars($)")+
  xlab("Products")+
  ggtitle("Top 10 Products vs Profit")+
  theme(plot.title = element_text(hjust = 0.5,size = 18,face = "bold"))
x + theme(axis.text.x =element_text(angle=90, hjust=1))

#=============================================================
# Top 10 products with quantityt

#sorted_superMkt <- Store_Data[order(-Store_Data$new_profit),]
#top_sorSuperMkt <- head(sorted_superMkt,10)
#bottom_sorSuperMkt <- tail(sorted_superMkt,10)

#top_sorSuperMkt
#bottom_sorSuperMkt

```

5.	Draw a multivariate graph for all the variables

```{r}

#=============================================================
# Multi variate analysis for Region, Product and Ship Mode

p <- ggplot(Store_Data, aes(x=Region, fill=Ship.Mode))+geom_bar()+ theme_bw() +labs(y="no. of products", title = "Region most products purchased")
p+theme(axis.text.x =element_text(angle=90, hjust=1) )

#=============================================================
# Multi variate analysis for Region, Product and Segment

p <- ggplot(Store_Data, aes(x=Region, fill = Segment))+geom_bar()+ theme_bw() +labs(y="no. of products", title = "Region most products purchased")
p+theme(axis.text.x =element_text(angle=90, hjust=1) )

#=============================================================
# Multi variate analysis for Region, Product and Sale

sale_pro <- Store_Data[,c('Region','Product.ID','Sales')]

sale <- as.character(sale_pro$Sales)
#sale <- substr(sale, 2, nchar(sale))
sale <- gsub("\\$", "", sale)
sale <- gsub(",","",sale)
sale <- as.numeric(sale)

sale_pro$NewSale <- sale
sale_pro$Sales <- NULL

d1 <- aggregate(NewSale~Region+Product.ID, data=sale_pro, FUN=sum) 
d2 <- d1[with(d1, order(-NewSale)), ]

RegionTop10Product<- head(d2,10)
RegionBottom10Product <- tail(d2,10)

RegionTop10Product
RegionBottom10Product

#=============================================================
# Multi variate analysis for Segment,Year,Sale and Profit

seg_data <- Store_Data[,c('Segment','Sales','Profit')]

prof <- as.character(Store_Data$Profit)
prof <- gsub("\\$","",prof)
prof <- gsub(",","",prof)
prof <- as.numeric(prof)

seg_data$NewSale <- sale
seg_data$NewProf <- prof

seg_data$Sales <- NULL
seg_data$Profit <-NULL

dt <- as.Date(Store_Data$Order.Date, format = "%d-%m-%y")
FuncYear <- function(a) as.integer(format(as.Date(a), "%Y"))
Y1 <- lapply(dt, function(y) FuncYear(y) )
Y1 <- as.vector(unlist(Y1))
seg_data$Year <- Y1

d1 <- aggregate(cbind(NewSale,NewProf) ~ Segment+Year, data=seg_data, FUN=sum) 

names(d1)[names(d1) == 'NewSale'] <- 'Sale'
names(d1)[names(d1) == 'NewProf'] <- 'Profit'

#Plot Year wise 
dat_l <- melt(d1, id.vars = c("Year", "Segment"))
p <- ggplot(data = dat_l, aes(x = Segment, y = value, group = variable, fill = variable))
p <- p + geom_bar(stat = "identity", width = 0.5, position = "dodge")
p <- p + facet_grid(. ~ Year)
p <- p + theme_bw()
p <- p + theme(axis.text.x = element_text(angle = 90))
p

#Plot Segment wise
dat_l <- melt(d1, id.vars = c("Segment", "Year"))
p <- ggplot(data = dat_l, aes(x = Year, y = value, group = variable, fill = variable))
p <- p + geom_bar(stat = "identity", width = 0.5, position = "dodge")
p <- p + facet_grid(. ~ Segment)
p <- p + theme_bw()
p <- p + theme(axis.text.x = element_text(angle = 90))
p

#=============================================================
# Multi variate analysis for Sales, Profit and categoty

profit <-  gsub("-.*", "", Store_Data$Profit)
profit <- gsub(",", "", Store_Data$Profit)
profit <- as.numeric(gsub("\\$", "", profit))

sales <- gsub(",", "", Store_Data$Sales)
sales <- as.numeric(gsub("\\$", "", sales))

Store_Data$new_sales <- sales
Store_Data$new_profit <- profit

names(Store_Data)[names(Store_Data) == 'new_sales'] <- 'Sale'
names(Store_Data)[names(Store_Data) == 'new_profit'] <- 'Profits'

ggplot(Store_Data, aes(Sale, Profits))+geom_point(aes(color=Sub.Category), alpha=0.5)+geom_smooth(method=lm)+facet_grid(~Category) + theme(axis.text.x = element_text(angle = 90))

#ggplot(Store_Data, aes(new_sales, new_profit))+geom_point(alpha=0.5)+geom_smooth(method=lm)+facet_grid(~Market) + theme(axis.text.x = element_text(angle = 90))

#=============================================================
# Multi variate analysis for Sales, Profit and sub-categoty

ggplot(Store_Data, aes(Sale, Profits))+geom_point()+geom_smooth(method=lm)+facet_grid(~Sub.Category)+ theme(axis.text.x = element_text(size = 4,angle = 90)) + theme(strip.text.x = element_text(size = 8, colour = "orange", angle = 90))

```
